%%%%%%%%%%%%%%%%%%%%%%acronym.tex%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% sample list of acronyms
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer Nature%%%%%%%%%%%%%%%%%%%%%%%%%%

\Extrachap{Glossary}

\runinhead{Abdominal aortic aneurysm} Localized dilation of the abdominal aorta, which can lead to rupture and severe complications if untreated.

\runinhead{Boundary condition} Condition that defines the values of variables in a physical system at the boundaries of a spatial domain to solve partial differential equations.

\runinhead{Broyden-Fletcher-Goldfarb-Shanno} Numerical optimization algorithm used to solve unconstrained minimization problems.

\runinhead{Computational fluid dynamics} Field that uses numerical methods to analyze and solve problems involving fluid flows.

\runinhead{Coronary Magnetic Resonance} Medical imaging technique based on magnetic resonance to visualize coronary blood flow and heart tissue.

\runinhead{Crank-Nicolson} Implicit numerical method used to solve parabolic and hyperbolic partial differential equations, often employed in CFD simulations.

\runinhead{Generalized minimal residual method} Iterative method for solving non-symmetric linear systems, widely used in CFD and other scientific computing fields.

\runinhead{Incremental pressure correction scheme} Numerical scheme for solving Navier-Stokes equations that separates velocity and pressure calculations into multiple steps.

\runinhead{Magnetic resonance imaging} Non-invasive medical imaging technique that uses magnetic fields and radio waves to produce detailed images of tissues inside the body.

\runinhead{Navier-Stokes} System of equations describing the motion of viscous fluids, fundamental in many fluid dynamics applications.

\runinhead{Oscillatory shear index} Measure of the directional oscillation of shear stress on the walls of a blood vessel, often associated with vascular disease susceptibility.

\runinhead{Partial differential equation} Equation involving partial derivatives of a function with respect to multiple variables, commonly used to model physical phenomena.

\runinhead{Root Mean Squared Error} Statistical measure of the difference between predicted and observed values, used to evaluate the accuracy of a model.

\runinhead{Time Averaged Wall Shear Stress} Time-averaged value of shear stress on vessel walls, relevant for studying hemodynamics.

\runinhead{Variational data assimilation} Method that combines mathematical models and observational data to improve estimates of physical states, commonly used in fluid dynamics and meteorology.

\runinhead{Wall shear stress} Stress exerted by a fluid on the wall of a vessel or conduit, crucial for analyzing hemodynamics and vascular diseases.